### 2016-12-20 R/ITHIM.Rmd
Worked on ITHIMList update

```{r foobar, eval = TRUE, echo = FALSE}
sumDALY <- function(ITHIM.baseline, ITHIM.scenario){
    return(sum(unlist(data.frame(compareModels(ITHIM.baseline,ITHIM.scenario)$daly.delta)[-1,]))) # AgeClass 1 is removed from totals
    }
```

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
stateVec <- c("CA","NY","WI","MI","OH") #c("CA","TX","NY","FL","VA","NC","AZ")
stateVecOrdered <- stateVec #c("NY","CA","WI","MI","OH") #c("NC","TX","VA","FL","AZ","NY","CA")

@@

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM()
ITHIM.default <- update(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- update(ITHIM.default, "cv", 1.65)
ITHIM.default <- update(ITHIM.default, "muNonTravel", 4)
ITHIM.default <- update(ITHIM.default, "muNonTravelMatrix", METmatrix)
ITHIM.default <- update(ITHIM.default, "quantiles", (1:99)/100)

for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- ITHIM.default
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], "muwt", muwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], "muct", muctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], "Rwt", RwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], "Rct", RctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], "GBD", gbdList[[HHSTATE]])
  }

@@

  for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], "muNonTravel", muNonTravel)
  }

>>>>

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
stateVec <- names(listOfLists) #c("CA","NY","WI","MI","OH") #c("CA","TX","NY","FL","VA","NC","AZ")
stateVec <- stateVec[stateVec != "ND"]
stateVecOrdered <- stateVec #c("NY","CA","WI","MI","OH") #c("NC","TX","VA","FL","AZ","NY","CA")

@@

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM()

ITHIM.default <- update(ITHIM.default, list( cvNonTravel = 3, cv = 1.65, muNonTravel = 4, muNonTravelMatrix = METmatrix, quantiles = (1:99)/100 ) )

ITHIM.national <- update(ITHIM.default, list(muwt = muwtNational, muct = muctNational, Rwt = RwtNational, Rct = RctNational))

for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- ITHIM.default
    ITHIMList[[HHSTATE]] <- update(ITHIM.default, list(muwt = muwtList[[HHSTATE]], muct = muctList[[HHSTATE]], Rwt = RwtList[[HHSTATE]], Rct = RwtList[[HHSTATE]], GBD = gbdList[[HHSTATE]]))
  }

@@

  for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- update(ITHIMList[[HHSTATE]], list(muNonTravel = muNonTravel))
  }
